### 2016-03-23 paper6.tex
Added initial draft of conclusions section.

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at the same url, as are the posterior distributions for the parameters fit in Section \ref{paper6_sec:mrd}. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.

>>>>

In the effort of open and reproducible research, we have made several data products freely available to the community. All of the reduced and telluric-corrected spectra used in this study are available at \url{https://zenodo.org/record/46340}. Samples of the primary and companion mass and system age posterior distributions are available at \url{https://zenodo.org/record/48073}, as are the posterior distributions for the parameters fit in Section \ref{sec:mrd} and every cross-correlation function generated in our analysis. We additionally provide a series of python libraries and jupyter notebooks with the computer code we used for the analysis on github: \url{https://github.com/kgullikson88/BinaryInference}.
